% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2011 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4paper]{article}

\usepackage{hyperref}
\usepackage{geometry}

\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\def\name{Oliver Kingshott}

\def\footerlink{http://oliver.kingshott.com/}

\hypersetup{
  colorlinks = true,
  urlcolor = magenta,
  pdfauthor = {\name},
  pdfkeywords = {computing, programming, hax},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

\markright{\name}
\thispagestyle{empty}

\usepackage{sectsty}
\sectionfont{\sffamily\mdseries\scshape\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

\setlength\parindent{0em}

\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

{\huge \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  Hookwood Farm, \\
  Puttenden Road, \\
  Tonbridge, \\
  Kent, \\
  United Kingdom. \\
  TN11 9QY
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone (UK): & +44 (0) 7835 873 851 \\
    Phone (USA): & +1 415 612 0695 \\
    Email: & \href{mailto:oliver@kingshott.com}{\tt oliver@kingshott.com} \\
    Web: & \href{http://oliver.kingshott.com/}{\tt oliver.kingshott.com} \\
  \end{tabular}
\end{minipage}

\section*{Summary}
\begin{itemize}
  \item Developed popular mobile and web applications using a wide range of different tools.
  \item Well versed in Python, Javascript, Objective-C, Java, Ruby and PHP. Good knowledge of system administration and computer security.
  \item Confident communicator \& public speaker.
\end{itemize}

\section*{Work}

\subsection*{Data Acquisition Developer - Skyscanner Ltd. (Summer 2011)}
\begin{itemize}
  \item Part of a team of 5 interns that increased airline coverage by 20\%, writing web scrapers with Python and MSSQL.
  \item Created a caching API for data acquisition team using Membase.
\end{itemize}

\subsection*{Loud Street Ltd. (2009-10)}
\begin{itemize}
  \item Co-founder, worked to create a social planner and event calendar. Interviewed by YCombinator. Eventually funded.
  \item Worked to develop ideas as a sole engineer.
  \item Expanded to bigger team, worked with an intern and another senior developer in building \& shipping the product.
\end{itemize}

\subsection*{Streamwire - Total IT Solutions (2007)}
\begin{itemize}
  \item IT services division of Serviced Office Group - \href{http://servicedofficegroup.com}{servicedofficegroup.com}.
  \item Worked alongside new IT director to manage inherited network infrastructure across multiple sites while providing front-line support to clients.
\end{itemize}

\subsection*{iFuse Technologies Ltd (2005 - 2007)}
\begin{itemize}
  \item Operations director at small web hosting company while still in high school. Sold in 2009.
  \item Oversaw sales \& marketing, customer service and coordinated technical operations, serving 50+ clients over both shared \& dedicated servers.
\end{itemize}

\section*{Projects}

\subsection*{Remote for Grooveshark - \href{http://gsremote.com}{gsremote.com}}
\begin{itemize}
\item Hobby project with a friend. Turns your phone into a remote control for the popular music service Grooveshark (2012 - Present).
\item Developed the iPhone / iPad app and website. Internationalized and localized the app into several languages. Support users and run advertising campaigns.
\item Tens of thousands of users, featured in "What's Hot" paid apps category on the iTunes app store worldwide.
\end{itemize}

\subsection*{Computing Society - \href{http://comp-soc.com}{comp-soc.com}}
\begin{itemize}
\item President of the University of Edinburgh Computing Society (2009). Raised membership from 30 to 250+ students.
\item Co-founded the Student Techmeetup, a monthly event which still attracts 50+ attendees \& industry speakers.
\item Received "Best New / Revamped Society" award from Edinburgh University Student Association.
\end{itemize}

\subsection*{Presentations}
\begin{itemize}
\item \emph{Orbited \& the Real Time Web} - Edinburgh Techmeetup (2009)
\item \emph{Introducing the Facebook API} - Barcamp Scotland (2010)
\item \emph{A brief history of things I've made} - Student Techmeetup (2012)
\end{itemize}

\subsection*{Awards}
\begin{itemize}
\item WWDC Student Scholarship (2013) - Winner of a free student ticket to WWDC for creating a video based Tamagotchi (named ``Oligotchi'') as part of their competition to create an autobiographical app. The app was completed in 5 days during final exams and received praise from judges for originality and creativity. 
\item NSConf 5 Student Scholarship (2013) - Winner of a free student ticket for extensive background in iOS development.
\end{itemize}

\subsection*{Miscellaneous}
\begin{itemize}
\item Volunteer administrator for the \href{http://www.tardis.ed.ac.uk/}{Tardis Project} (2008 - present) - a self-run UNIX computing service for students. Vetted, created \& supported many new accounts, in part reviving the project.
\item Publicity Secretary for \href{http://facebook.com/getjumped/}{Edinburgh University Skydiving Club} (2010 - 2012), putting 100 students on First Jump Courses each year.
\end{itemize}

\section*{Education}
\begin{itemize}
  \item Computer Science BSc (Hons), 2:1 from the University of Edinburgh, UK. Graduated 2013. 
  \item A levels in Maths, Physics, and Information Technology (AAB) from MPW, Cambridge, UK.
\end{itemize}

\section*{Personal}

\begin{itemize}
\item British / Australian citizen
\item Full drivers license
\item FAI A licensed Parachutist
\item References available upon request.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
